Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-11-28 paper/dcpo_gender_roles.Rmd
update

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))

@@

Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender].
With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes.
Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures.
Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.

To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a]. 
Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations. 
The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].

This article proceeds with the following order. 
First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector.
Next, we illustrate the data source we used to build our index.
Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced.
Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.

# Multi-Dimensionality in Egalitarian Gender Role

@@

We classified the available survey items on gender egalitarian attitudes into four categories.  
The first of these categories consists of questions asking respondents' views on women gaining opportunities in the traditionally masculine public sphere of education, paid work, and politics.
The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only very rarely included in surveys.
The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition of various forms of sexual harassment to the justifiability of intimate partner violence committed by husbands.

@@

@@

@@

To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.
Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

@@

polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)

housewifefull4_cy <- dcpo_input_raw_public1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
```

Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of the twelve most-commonly asked items are available.
The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r round(polileader4_cy*100/(n_countries * n_years))`% of the `r total_cy` total possible country-years covered---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.

@@

```{r dcpo, eval=FALSE}
iter <- 4000

@@

@@

```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, Most Recent Available Year \\label{cs_2020}", fig.height=8, warning=FALSE}
load(here::here("data", "dcpo_input_public.rda"))
load(here::here("data", "dcpo_output.rda"))

@@

p1_data_a <- p1_data %>% 
  filter(half==2) %>% 
  mutate(ranked = as.factor(row_number(mean)))
p1_data_b <- p1_data %>%
  filter(half==1) %>%
  mutate(ranked = as.factor(row_number(mean)))

>>>>

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))

@@

<!-- Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender]. -->
<!-- With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants. -->
<!-- For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined. -->
<!-- However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes. -->
<!-- Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures. -->
<!-- Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004. -->

<!-- To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a].  -->
<!-- Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations.  -->
<!-- The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis. -->
<!-- The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors. -->
<!-- We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role. -->
<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women]. -->
<!-- Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender]. -->

<!-- This article proceeds with the following order.  -->
<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
<!-- Next, we illustrate the data source we used to build our index. -->
<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->

# Multi-Dimensionality in Gender Egalitarianism

@@

@@

n_cy <- dcpo_input_raw_public1 %>%
  distinct(country, year) %>% 
  nrow() %>% 
  scales::comma()

@@

spanned_cy <- dcpo_input_raw_public1 %>% 
  group_by(country) %>% 
  summarize(years = max(year) - min(year)) %>% 
  summarize(n = sum(years)) %>% 
  pull(n) %>% 
  scales::comma()

@@

We classified the available survey items on gender egalitarian attitudes into four categories.  
The first of these categories consists of questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
The second category, in turn, encompasses questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare.
A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys.^[One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.

To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
The complete list of gender egalitarianism items is included in the Appendix.]
Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

@@

polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
```

Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of the twelve most-commonly asked items are available.
The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the `r spanned_cy` country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.

@@

```{r dcpo, eval=FALSE}
iter <- 3000

dcpo_input <- dcpo_input_public

@@

save(dcpo_input, file = here::here("data", "dcpo_input.rda"))

@@

```{r cs_plot, fig.cap="Public Gender Egalitarianism, Most Recent Available Year \\label{cs_mry}", fig.height=8, warning=FALSE}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_output.rda"))

@@

p1_data_a <- p1_data %>% 
  filter(half==2) %>% 
  mutate(ranked = as.factor(row_number(mean)))
p1_data_b <- p1_data %>%
  filter(half==1) %>%
  mutate(ranked = as.factor(row_number(mean)),
         country = str_replace(country, "’", "'"))
